Measuring starspot properties by forward modeling IGRINS spectra of \name

### 2016-07-06 document/ms.tex
Some edits to the results section, some new text to results, moving on to the two temperature results

It is clear that the single-temperature model is a poor fit to the data.  Our model assumptions were incorrect: no single temperature can describe all the spectral lines present in the spectra.  This discrepancy is circumstantial evidence for the direct detection of spectral lines attributable to starspots.  This circumstantial evidence should not be surprising, given the previous evidence that \name possesses a large coverage fraction of starspots \citep{2014MNRAS.444.3220D}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase}.

% Comparing the single-component results from Optical to Infrared
Note that some care should be taken when directly comparing results between the ESPaDoNs and IGRINS spectra since they were not taken at the same time.  These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.  If we assume the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, we can derive the result that the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.

We can understand the heightened sensitivity to starspot spectral lines as wavelength increases in the following way.  The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission.  So the ratio flux density as function of wavelength will generally increase with wavelength.  In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.  The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K with solar metalicity and $\logg=3.5$.  The flux density ratio is the flux per solid angle, so the delivered flux ratio will depend on (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.

@@

\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  These would end up being closer to the best fit values.}

We performed a further plausibility check to constrain the effect size of starspots.  We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.  We coadded the spectra in a mixture model:  $ \mathsf{M}_{mix} = c \cdot \mathsf{M}_A(T_\textrm{eff,A}) + (1-c) \cdot \mathsf{M}_B(T_\textrm{eff,B})$.  We chose a fill factor of starspots of 30\%.  We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters one would na\"{\i}vely derive.  The noised-up optical data yields $\teff \sim 4100$ K, close to that of the A component.
\comm{I don't think I ever put together a figure for this, should we just skip it?  I think so.}

We want to measure the derived effective temperature as a function of wavelength.  The motivation for this strategy is as follows.  We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots citeXX.  Such a photosphere will have an emergent spectrum composed of superpositions of relatively cool patches and warm patches.  The visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.  The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches citeXX.

The fit of a single-temperature forward-modeled spectrum to different regions of the spectrum could therefore conceivably yield different estimates for the effective temperature.

In principle, one could estimate the effective temperature \emph{evaluated independently for each spectral line}.  The line strength is often degenerate with other properties (\emph{e.g.} magnetic field, $\log{g}$, $[\mathrm{Fe}/\mathrm{H}]$, etc.), but \emph{on average} these correlations would be averaged over.

We measured the effective temperature in \emph{each of the 43 spectral orders} of IGRINS.  Figure \ref{fig:teffOrder} plots each derived effective temperature value and uncertainty at the center position of each order.

@@

>>>>

It is clear that the single-temperature model is a poor fit to the data.  Our model assumptions were incorrect: no single temperature can describe all the spectral lines present in the spectra.  This discrepancy is circumstantial evidence for the direct detection of spectral lines attributable to starspots.  This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{2014MNRAS.444.3220D}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase} and discussed previously by \citet{grankin08}.

We performed a further plausibility check to constrain the effect size of starspots.  We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.  We coadded the spectra in a mixture model:  $ \mathsf{M}_{mix} = c \cdot \mathsf{M}_A(T_\textrm{eff,A}) + (1-c) \cdot \mathsf{M}_B(T_\textrm{eff,B})$.  We chose a fill factor of starspots of 30\%.  We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters our full-spectrum fitting procedure would na\"{\i}vely derive.  
\comm{I don't think I ever put together a figure for this, should we just skip it?  I think so.}

\subsection{Heightened sensitivity to starspot spectral lines in the infrared}

Some care should be taken when directly comparing results between the ESPaDoNs and IGRINS spectra since they were not taken at the same time.  These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.  If we assume the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, we can derive the result that the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.  The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.

We can understand the heightened sensitivity to starspot spectral lines as wavelength increases in the following way.  The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.  So the ratio of flux density between starspot and bulk photosphere as function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail.  In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.  The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K with solar metalicity and $\logg=3.5$.  The flux density ratio is the flux per solid angle, so the delivered flux ratio for a finite sized starspot will depend on the (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.

@@

\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  -These would end up being closer to the best fit values.}

In summary, the visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.  The infrared spectrum will have a lower overall spot contast, but will have higher relative contribution attributable to the cool patches.  This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{2008ApJ...687L.103P}.  
\comm{This blurb should probably go in the introduction.}

@@

Motivated by the failure of single-temperature model full-spectrum fitting, we added two new model parameters our forward model: a starspot temperature and a fill factor, as described by Equation \ref{eqn:Mix_M}.  We also altered the model as described in Section \ref{sec:methods} and detailed in Appendix \ref{methods-details}.
